A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2021-08-02 analysis/article.Rmd
refactor: use bookdown::html_document2 instead of workflowr::wflow_html to allow crossreferences

---
editor_options:
  chunk_output_type: console
title: "A Model to Predict Survival in Patients with End-Stage Liver Disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Background**:
      TODO

@@

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
output:
  workflowr::wflow_html:
    pandoc_args:
      - --filter=pandoc-crossref
        # pandoc_args doesn't support r evaluation
      - "--lua-filter=pandoc/lua-filters/scholarly-metadata.lua"
      - "--lua-filter=pandoc/lua-filters/author-info-blocks.lua"
---

>>>>

---
# R markdown template taken from
# Dan Holmes <dtholmes@mail.ubc.ca>
# https://labrtorian.com/2019/08/26/rmarkdown-template-that-manages-academic-affiliations/
editor_options:
  chunk_output_type: console
title: "A Model to Predict Survival in Patients with End-Stage Liver Disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Background**:
      TODO

@@

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
output:
  bookdown::html_document2:
    pandoc_args:
        # pandoc_args doesn't support r evaluation
      - "--lua-filter=pandoc/lua-filters/scholarly-metadata.lua"
      - "--lua-filter=pandoc/lua-filters/author-info-blocks.lua"
---
